## Homework 4

<!--
Remember you can use the example4.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework4.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->

Step one is to read in the data for the Homework4 Assignment.
```{r}
dat<-read.csv("homework4.csv")
```
<!--
Check the structure of the data.
-->

The next step is to check the structure of the Homework 4 Assignment.
```{r}
str(dat)
```
From the data we can see that there are two variables condition and agreement. 
<!--
Create a table that shows how many people fell into each category.
-->

Next step is to create a table showing how many participants fell into each of the conditions so we can see if there may be a relationship or if they are independent from each other.
```{r}
table(dat$condition, dat$agreement)
```
From the data we can see that more participants in the experimental group answered yes (26) compared to no (14). The control group had equal responses to yes (20) and no (20). 

<!--
Perform a chi-square test to determine whether or not the experimental
conditions and agreement with a statement are independent or related.
Also, interpret the results of your test and provide a a statistical
statement that supports your interpretation. As there's no way to
insert the chi-square symbol, you can just use chi-square instead
(see example4.Rmd).
-->

Next I performed a chi-square test to determine whether or not the experimental condition and agreement with a statement are independent or related.
```{r}
chisq.test(dat$condition,dat$agreement)
```
According to the results of the chi-square test, the experimental condition and agreement with statement are independent of one another Chi-square = 1.3, p = .26